\documentclass[../main.tex]{subfiles}

Unlike most other labs, this lab will be worth 30 points total in your grade and is graded as follows:\\

Lab 5 Postlab: 20 points (Engineering, Team)

Lab 5 Maps and Figures: 10 points (Technical Communication)\newline
\newline
Keep technical communication lectures in mind while making your maps in figures.\newline 

\subsection*{Engineering Points}
Turn in \texttt{.txt} files for all code written, and one
\texttt{.pdf} for your postlab questions as follows. 

\begin{enumerate}
  \item All 3 Arduino programs that were created for this lab (AS
    \texttt{.txt} FILES, YOU WILL RECEIVE NO POINTS FOR
    \texttt{.ino} FILES). 
  \item All GPS KML and LOG data (AS \texttt{.txt} FILES).
  \item All MATLAB (or Python) code used to process the GPS information (AS
    \texttt{.txt} FILES).
  \item Answers to the post lab questions (AS \texttt{.pdf} FILE).
\end{enumerate}

(Sorry to have to make you convert to \texttt{.txt}. Canvas doesn't
allow previews of \texttt{.ino}, \texttt{.py}, and a lot of
other file types so conversion to \texttt{.txt} is required for us to
grade you. You can export to \texttt{.txt} through the IDE.)

\section*{Technical Communication}

Keep technical communication lectures in mind while making your maps in
figures. Among other things, be sure to:
\begin{enumerate}
  \item Print your MATLAB or Python figures to png of jpg, do not use screencaps
  \item Include all necessary titles and axis labels
  \item Colors are your friend! Use them effectively

\end{enumerate}

