\documentclass[../main.tex]{subfiles}

\textbf{These videos are extremely helpful. We \textit{VERY} STRONGLY recommend you watch these to succeed.}

We developed three videos for you to complete this lab, along with supplemental videos for topics you may be unfamiliar with. This lab can be very, very frustrating if you don't pay careful attention to what we described in these videos. 

\begin{itemize}
  \item \href{https://www.youtube.com/watch?v=sVK2D9JSnXA}{`Pointers \& Arrays
    (Part 1)' is a supplemental mini lesson on pointers. Our starter code
  expects you to have a basic understanding of pointers, so if you don't (or you
need a refresher), please watch this video. }

  \item
    \href{https://www.youtube.com/watch?v=cPrvM4rRVHo&list=PLp2z0IQxLSvnRLMU8Tr3Pw0gq9NoPankb&index=1}{`Arduino
    Lab 5a: GPS Modules, Part 1' helps you wire your board up and verify it is
  working}

  \item
      \href{https://www.youtube.com/watch?v=KS2mlpPaEUw&list=PLp2z0IQxLSvnRLMU8Tr3Pw0gq9NoPankb&index=2}{`Arduino
      Lab 5a: GPS Modules, Part 2' guides you through the starter code and gives
    you advice on completing tasks. \textbf{This part of the lab will take you
  the longest, so it's worthwhile to watch this video in its entirety.}}

  \item For plotting your maps, you have a choice of implementing this code in either MATLAB or Python.
    \begin{itemize}
      \item \href{https://www.youtube.com/watch?v=l3WMY8j0Z50&list=PLp2z0IQxLSvnRLMU8Tr3Pw0gq9NoPankb&index=3}{If you want to use MATLAB, you will be completing Lab 5b parts 1 and 2. Click here for a link to part 1.}
      \item \href{https://www.youtube.com/watch?v=FLlHRjw5sDA&list=PLp2z0IQxLSvnRLMU8Tr3Pw0gq9NoPankb&index=5}{If you want to use Python, you will be completing Lab 5c. Click here for the video.}
    \end{itemize}
\end{itemize}


